\documentclass[aps,prc,reprint,groupedaddress]{revtex4-2}


\begin{document}

%Title of paper
\title{Independent confirmation of an isomeric state in $^{273}\text{Ds}$ and its decay properties via the $^{238}\text{U}(^{40}\text{Ar},5n)$ reaction}

% repeat the \author .. \affiliation  etc. as needed
\author{Z.R.Sun} % 请替换为实际作者姓名
\affiliation{Institute of Modern Physics, Chinese Academy of Sciences (IMP CAS), Lanzhou, China}

\date{\today}

\begin{abstract}
An extensive series of experiments was performed at the SHANS-2 separator at IMP CAS.  First, the cross section of the $^{238}\text{U}(^{40}\text{Ar},5n)^{273}\text{Ds}$ reaction was measured in the excitation-energy range from 42 to 51 MeV.Previously, the same reaction was studied in the JINR-IMP CAS collaborative experiment at the DGFRS-2 separator at the energy of 49 MeV. In those experiments, two decay chains of $^{273}\text{Ds}$ were observed, and two decays from different energy levels with different energies and lifetimes were found, indicating the existence of an isomeric level in addition to the ground-state one.  In the experiments at SHANS-2, the entire energy range was studied in detail at excitation energies of 40, 45, and 50 MeV, and the upper cross-section limits of 833, 1118, and 511 fb, respectively, were set.  But at 49.5 MeV, two decay chains of $^{273}\text{Ds}$ with a cross section of $219_{-147}^{+292}$ fb was measured.  In the experiment at DGFRS-2, the production cross section of this isotope was $180_{-120}^{+440}$ fb. Transitions from different energy levels were also observed at SHANS-2 in the two new chains. 
\end{abstract}

%\maketitle must follow title, authors, abstract, and keywords
\maketitle

\section{Introduction}

Superactinides are generally considered to be elements with $Z \ge 104$. According to the liquid drop model, these elements should not exist~\cite{Hahn1939}. Currently, the academic community believes that the existence of such superheavy elements is related to the nuclear shell structure. The predicted limits of nuclear survival lie at the closed nuclear shells of protons $Z=108$ and neutrons $N=162$ (deformed nuclei)~\cite{Smolanczuk1995}, as well as the emergence of heavier (superheavy) nuclei with $Z=114-126$ and $N=184$~\cite{Oganessian2015}. As an odd-neutron nucleus with a single particle on the $N=162$ shell, $^{273}\text{Ds}$ and its decay product $^{269}\text{Hs}$, which is an odd-neutron nucleus with a hole below the $N=161$ shell, are of great importance for gaining deeper insights into the $N=162$ shell.

$^{273}\text{Ds}$ was first unambiguously observed as a decay product in cold fusion experiments at the SHIP facility at GSI~\cite{Ninov1996}. It is worth noting that in the cold fusion reaction $^{208}\text{Pb}(^{70}\text{Zn},n)^{277}\text{Cn}$ conducted at GSI~\cite{Ninov1996, Hofmann2002} and RIKEN~\cite{Morita2007, Sumita2013}, the lifetime of $^{273}\text{Ds}$ as a decay product is on the order of 0.1 ms. Last year, in the $^{238}\text{U}(^{40}\text{Ar}, 5n)^{273}\text{Ds}$ experiment conducted by Yu. Ts. Oganessian \textit{et al.}~\cite{Oganessian2024} at the DGFRS-2 separator~\cite{Oganessian2022}, two decay chains were discovered where $^{273}\text{Ds}$ was produced directly. These were identified using the genetic correlation method~\cite{Hofmann2018}. One chain is consistent with historical data, while the other was assigned to an isomeric state of $^{273}\text{Ds}$. Unfortunately, both chains are incomplete, and little is known about the decay information of $^{269}\text{Hs}$.

Subsequently, Z. Wang \textit{et al.} performed theoretical calculations on the decay pathways of these two chains using the density-dependent cluster model (DDCM) and the unified decay formula (UDF)~\cite{Wang2024}, proposing minor modifications to these two chains. The present work was carried out at SHANS-2~\cite{Sheng2021}, where two additional distinct decay pathways were observed using the same reaction. The pathway information is complete and consistent with historical data through the genetic correlation method~\cite{Hofmann2018}, which fully and independently confirms the authenticity of the two states of $^{273}\text{Ds}$ ($^{273}\text{Ds}^{a}$ and $^{273}\text{Ds}^{b}$) observed by Yu. Ts. Oganessian \textit{et al.}~\cite{Oganessian2024}.

The experiment is described below in Table~\ref{tab:table1}, and the experimental data are presented.

\bibliography{Ds273}
\end{document}